Time series clusters, k = 9

### 2021-03-22 src/LAs_Clusters_k9.Rmd
ET changes / responses to reviewer comments

```{r upload regression , results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

@@

aux.up <- multinom(cluster.up ~ 
                     #pop16_64 + # non sign, while pop is
                     pop +
                     #pop.dens + 
                     job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                     distMet + distLondon + south +
                     managers + tech + skilled + prof + admin + caring + plant +
                     earnings + I(total.busi/pop) + nvq4 + I(furlough/pop) +
                     I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                     virgin
                   , data = data, 
                   trace = F) # to avoid messages

stargazer(aux.up, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
            "pop, 2018",
            #"pop. density, 2018",
            "job density, 2018",
            "distance to nearest met. area",
            "distance to London",
            "South of the UK",
            "% of managerial jobs, 2020",
            "% of tech jobs, 2020",
            "% of skilled trade jobs, 2020",
            "% of professional jobs, 2020",
            "% of administrative jobs, 2020",
            "% of leisure jobs, 2020",
            "% of machine operation jobs, 2020",
            "earnings, 2019",
            "n. business est. per hab., 2019",
            "% of NVQ4+",
            "% furloughed pop., 2020",
            "n. of AM broadband tests per hab., 2020",
            "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs
                              , n.obs, n.obs))))

@@

```{r upload regression no NVQ4, results= 'asis', message=F, error=F, warning=F}
aux.up <- multinom(cluster.up ~ 
                     #pop16_64 + # non sign, while pop is
                     pop +
                     #pop.dens + 
                     job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                     distMet + distLondon + south +
                     managers + tech + skilled + prof + admin + caring + plant +
                     earnings + I(total.busi/pop) + I(furlough/pop) +
                     I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                     virgin
                   , data = data, 
                   trace = F) # to avoid messages

@@

aux.up <- multinom(cluster.up ~ 
                     #pop16_64 + # non sign, while pop is
                     pop +
                     #pop.dens + 
                     job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                     distMet + distLondon + south +
                     managers + tech + skilled + admin + caring + plant +
                     earnings + I(total.busi/pop) + nvq4 + I(furlough/pop) +
                     I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                     virgin
                   , data = data, 
                   trace = F) # to avoid messages

stargazer(aux.up, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
            "pop, 2018",
            #"pop. density, 2018",
            "job density, 2018",
            "distance to nearest met. area",
            "distance to London",
            "South of the UK",
            "% of managerial jobs, 2020",
            "% of tech jobs, 2020",
            "% of skilled trade jobs, 2020",
            #"% of professional jobs, 2020",
            "% of administrative jobs, 2020",
            "% of leisure jobs, 2020",
            "% of machine operation jobs, 2020",
            "earnings, 2019",
            "n. business est. per hab., 2019",
            "% of NVQ4+",
            "% furloughed pop., 2020",
            "n. of AM broadband tests per hab., 2020",
            "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs
                              , n.obs, n.obs))))

>>>>

```{r upload regression, results= 'asis', message=F, error=F, warning=F}

# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

@@

aux.up.v1 <- multinom(cluster.up ~ 
                     #pop16_64 + # non sign, while pop is
                     pop +
                     #pop.dens + 
                     job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                     distMet + distLondon + south +
                     managers + tech + skilled + prof + admin + caring + plant +
                     earnings + I(total.busi/pop) + nvq4 + I(furlough/pop) +
                     I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                     virgin
                   , data = data, 
                   trace = F) # to avoid messages

# McFadden's R squared
aux.up.v1.null <- multinom(cluster.up ~ 1, data = data)
r2.up.v1 <- 1-logLik(aux.up.v1)/logLik(aux.up.v1.null)

n.obs <- dim(aux.up.v1$fitted.values)[1]

stargazer(aux.up.v1, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
            "pop, 2018",
            #"pop. density, 2018",
            "job density, 2018",
            "distance to nearest met. area",
            "distance to London",
            "South of the UK",
            "% of managerial jobs, 2020",
            "% of tech jobs, 2020",
            "% of skilled trade jobs, 2020",
            "% of professional jobs, 2020",
            "% of administrative jobs, 2020",
            "% of leisure jobs, 2020",
            "% of machine operation jobs, 2020",
            "earnings, 2019",
            "n. business est. per hab., 2019",
            "% of NVQ4+",
            "% furloughed pop., 2020",
            "n. of AM broadband tests per hab., 2020",
            "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up.v1[1],3), round(r2.up.v1[1],3), round(r2.up.v1[1],3),
                             round(r2.up.v1[1],3), round(r2.up.v1[1],3), round(r2.up.v1[1],3),
                             round(r2.up.v1[1],3), round(r2.up.v1[1],3), round(r2.up.v1[1],3)
                             , round(r2.up.v1[1],3), round(r2.up.v1[1],3)),
                           (c("N",
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs
                              , n.obs, n.obs))))

@@

```{r upload regression no NVQ4, results= 'asis', message=F, error=F, warning=F}

# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

aux.up <- multinom(cluster.up ~ 
                     #pop16_64 + # non sign, while pop is
                     pop +
                     #pop.dens + 
                     job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                     distMet + distLondon + south +
                     managers + tech + skilled + prof + admin + caring + plant +
                     earnings + I(total.busi/pop) + I(furlough/pop) +
                     I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                     virgin
                   , data = data, 
                   trace = F) # to avoid messages

@@

aux.up.noprof <- multinom(cluster.up ~ 
                     #pop16_64 + # non sign, while pop is
                     pop +
                     #pop.dens + 
                     job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                     distMet + distLondon + south +
                     managers + tech + skilled + admin + caring + plant +
                     earnings + I(total.busi/pop) + nvq4 + I(furlough/pop) +
                     I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                     virgin
                   , data = data, 
                   trace = F) # to avoid messages

# McFadden's R squared
aux.up.noprof.null <- multinom(cluster.up ~ 1, data = data)
r2.up.noprof <- 1-logLik(aux.up.noprof)/logLik(aux.up.noprof.null)

n.obs <- dim(aux.up.noprof$fitted.values)[1]

stargazer(aux.up.noprof, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
            "pop, 2018",
            #"pop. density, 2018",
            "job density, 2018",
            "distance to nearest met. area",
            "distance to London",
            "South of the UK",
            "% of managerial jobs, 2020",
            "% of tech jobs, 2020",
            "% of skilled trade jobs, 2020",
            #"% of professional jobs, 2020",
            "% of administrative jobs, 2020",
            "% of leisure jobs, 2020",
            "% of machine operation jobs, 2020",
            "earnings, 2019",
            "n. business est. per hab., 2019",
            "% of NVQ4+",
            "% furloughed pop., 2020",
            "n. of AM broadband tests per hab., 2020",
            "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up.noprof[1],3), round(r2.up.noprof[1],3), round(r2.up.noprof[1],3),
                             round(r2.up.noprof[1],3), round(r2.up.noprof[1],3), round(r2.up.noprof[1],3),
                             round(r2.up.noprof[1],3), round(r2.up.noprof[1],3), round(r2.up.noprof[1],3)
                             , round(r2.up.noprof[1],3), round(r2.up.noprof[1],3)),
                           (c("N",
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs,
                              n.obs, n.obs, n.obs
                              , n.obs, n.obs))))

### 2021-03-22 src/descriptive_Clusters.Rmd
ET changes / responses to reviewer comments

#create time variation plots for speedtests for each year
Tests19 <- count(TS2019, date)
TS2019 <- left_join(TS2019, Tests19)
names(TS2019)[13] <- "test frequency 2019"
time.var.plot2019 <- timeVariation(TS2019, pollutant = "test frequency 2019", statistic = "mean")
Tests20 <- count(TS2020, date)
TS2020 <- left_join(TS2020, Tests20)
names(TS2020)[13] <- "test frequency 2020"
time.var.plot2020 <- timeVariation(TS2020, pollutant = "test frequency 2020", statistic = "mean")

#export time variation plots for paper
out.plot <- paste(path, "/paper/v1/figures/time.var.plot2019.png", sep = "")
png(out.plot)
time.var.plot2019
dev.off()

out.plot <- paste(path, "/paper/v1/figures/time.var.plot2020.png", sep = "")
png(out.plot)
time.var.plot2020
dev.off()

@@

#export UpClusterL plot for paper
out.plot <- paste(path, "/paper/v1/figures/UpCluster.png", sep = "")
png(out.plot)
UpClusterL
dev.off()

@@

#export UpClusterS plot for paper
#out.plot <- paste(path, "/paper/v1/figures/UpClusterS.png", sep = "")
#png(out.plot)
#UpClusterS
#dev.off()

#summarise download speed clusters by hour of each weekday and plot
cluster.down <- TS2020 %>%
  group_by(cluster.down, weekday, hour) %>%
  summarise(mean.down = mean(speeddown))
names(cluster.down)[1] <- "clusterID"
names(LAD.cluster.down)[1] <- "clusterID"
cluster.down <- left_join(cluster.down, LAD.cluster.down)
cluster.down <- cluster.down[which(cluster.down$down.LADs > 5),]
cluster.down$clusterID <- as.factor(cluster.down$clusterID)
#add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2020, month = 3, day = 2),
  make_datetime(year = 2020, month = 3, day = 3),
  make_datetime(year = 2020, month = 3, day = 4),
  make_datetime(year = 2020, month = 3, day = 5),
  make_datetime(year = 2020, month = 3, day = 6)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.down <- merge(cluster.down, help.dates, by = "weekday")
cluster.down$hour <- paste(cluster.down$hour, ":00", sep="")
cluster.down$help.date.time <- with(cluster.down, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
#plot cluster statistic for mean download speeds
TestCluster <- ggplot(cluster.down, aes(help.date.time, mean.down, 
                                         colour = clusterID))
TestCluster + geom_line() + labs(x = "Weekdays March-May") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + geom_point()

>>>>

#create time variation plots for speedtests for each year
Tests19 <- count(TS2019, date)
TS2019 <- left_join(TS2019, Tests19)
names(TS2019)[13] <- "test frequency 2019"
time.var.plot2019 <- timeVariation(TS2019, pollutant = "test frequency 2019", statistic = "mean",
                                   par.settings=list(fontsize=list(text=8)))
Tests20 <- count(TS2020, date)
TS2020 <- left_join(TS2020, Tests20)
names(TS2020)[13] <- "test frequency 2020"
time.var.plot2020 <- timeVariation(TS2020, pollutant = "test frequency 2020", statistic = "mean",
                                   par.settings=list(fontsize=list(text=8)))

#export time variation plots for paper
out.plot <- paste(path, "/paper/v2_taylor_francis/figures/time.var.plot2019.png", sep = "")
png(out.plot)
time.var.plot2019
dev.off()

out.plot <- paste(path, "/paper/v2_taylor_francis/figures/time.var.plot2020.png", sep = "")
png(out.plot)
time.var.plot2020
dev.off()

@@

#export UpClusterL plot for paper
out.plot <- paste(path, "/paper/v2_taylor_francis/figures/UpCluster.png", sep = "")
UpCluster
ggsave(out.plot)

@@

# The figure with the small clusters is no included in the paper
#export UpClusterS plot for paper
#out.plot <- paste(path, "/paper/v2_taylor_francis/figures/UpClusterS.png", sep = "")
#png(out.plot)
#UpClusterS
#dev.off()

# Not used in the paper
#summarise download speed clusters by hour of each weekday and plot
cluster.down <- TS2020 %>%
  group_by(cluster.down, weekday, hour) %>%
  summarise(mean.down = mean(speeddown))
names(cluster.down)[1] <- "clusterID"
names(LAD.cluster.down)[1] <- "clusterID"
cluster.down <- left_join(cluster.down, LAD.cluster.down)
cluster.down <- cluster.down[which(cluster.down$down.LADs > 5),]
cluster.down$clusterID <- as.factor(cluster.down$clusterID)
#add fake dates for plotting
help.dates <- tibble(help.date.time = c(
  make_datetime(year = 2020, month = 3, day = 2),
  make_datetime(year = 2020, month = 3, day = 3),
  make_datetime(year = 2020, month = 3, day = 4),
  make_datetime(year = 2020, month = 3, day = 5),
  make_datetime(year = 2020, month = 3, day = 6)),
                     weekday = c("Mon", "Tue", "Wed", "Thu", "Fri"))
cluster.down <- merge(cluster.down, help.dates, by = "weekday")
cluster.down$hour <- paste(cluster.down$hour, ":00", sep="")
cluster.down$help.date.time <- with(cluster.down, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
#plot cluster statistic for mean download speeds
TestCluster <- ggplot(cluster.down, aes(help.date.time, mean.down, 
                                         colour = clusterID))
TestCluster + geom_line() + labs(x = "Weekdays March-May") + 
  scale_x_datetime(breaks = as.POSIXct(c("2020-03-02 15:00:00", 
                    "2020-03-03 15:00:00", "2020-03-04 15:00:00",
                    "2020-03-05 15:00:00", "2020-03-06 15:00:00"), 
                    labels = "%a"), labels = 
                     c("Mon", "Tues", "Weds", "Thurs", "Fri")) + geom_point()

### 2021-03-22 src/ts_clusters_k9.Rmd
ET changes / responses to reviewer comments

```{r settings, include = FALSE}
library(tsbox)
library(ggplot2)
library(tidyverse)
library(geojsonio)
library(tsfeatures)
library(rprojroot)
library(openair)
library(reshape2)
library(lubridate)
library(rgdal)
library(maptools)
library(sp)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(knitr)
library(rprojroot)
library(viridis)
library(hrbrthemes)
library(imputeTS)
library(tsbox)
library(dtwclust)
library(leaflet)
library(ggmap)
library(cowplot)

@@

# source: https://data.gov.uk/dataset/7c387c64-d25f-474a-b07e-b933578caea2/local-authority-districts-april-2019-boundaries-uk-bfe

@@

# ggplot2 maps
la.f <- fortify(la, region = "lad19nm")
la.f <- merge(la.f, clusters.nodiff, by.x = "id", by.y = "LAD")
la.f <- la.f[order(la.f$order),] # if i don't order merge.nuts.f loses order and the map has gaps

ggplot(la.f, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.tests))) +
  #theme_nothing(legend = TRUE) +
  labs(title = "Test clusters") +
  scale_fill_viridis_d()+
  guides(fill=guide_legend(title="Clusters")) +
  theme_void()

ggplot(la.f, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.up))) +
  #theme_nothing(legend = TRUE) +
  labs(title = "Upload clusters") +
  scale_fill_viridis_d()+
  guides(fill=guide_legend(title="Clusters")) +
  theme_void()

#ggsave("all_maps2.png") # this is the colour map for the preprint
# out.path.map <- paste0(path, "/paper/v1/figures/map.up.clusters9.png")
# ggsave(out.path.map)#,
#width = 210, #A4
#height = 297, #A4
#units = "mm")
```

```{r, eval=FALSE}
# leaflet maps

>>>>

```{r settings, include = FALSE}
library(tsbox)
library(ggplot2)
library(tidyverse)
library(geojsonio)
library(tsfeatures)
library(rprojroot)
library(openair)
library(reshape2)
library(lubridate)
library(rgdal)
library(maptools)
library(sp)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(knitr)
library(rprojroot)
library(viridis)
library(hrbrthemes)
library(imputeTS)
library(tsbox)
library(dtwclust)
library(leaflet)
library(ggmap)
library(cowplot)
library(ggrepel)
library(maps)
library(gridExtra)

@@

# source: https://data.gov.uk/dataset/7c387c64-d25f-474a-b07e-b933578caea2/local-authority-districts-april-2019-boundaries-uk-bfe
# also saved locally \data\raw\Local_Authority_Districts_(December_2019)_Boundaries_UK_BGC.geojson

@@

# ggplot2 maps
la.f <- broom::tidy(la, region = "lad19nm")
la.f <- merge(la.f, clusters.nodiff, by.x = "id", by.y = "LAD")
la.f <- la.f[order(la.f$order),] # if i don't order merge.nuts.f loses order and the map has gaps

# ggplot(la.f, aes(x = long, y = lat)) +
#   geom_polygon(aes( group = group, fill = as.factor(cluster.tests))) +
#   #theme_nothing(legend = TRUE) +
#   labs(title = "Test clusters") +
#   scale_fill_viridis_d()+
#   guides(fill=guide_legend(title="Clusters")) +
#   theme_void()

# using world.cities from `maps`
cities <- world.cities %>% filter(country.etc=="UK")

ggplot(la.f, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.up))) +
  #labs(title = "Upload clusters") +
  scale_fill_brewer(palette="Set1", 
                    direction = -1) +
  geom_text_repel( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat, label=name), size=4) +
  geom_point( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat), color="black", size=1) +
  guides(fill=guide_legend(title="Clusters")) +
  theme_void()

# Run only if needed
# out.path.map <- paste0(path, "/paper/v2_taylor_francis/figures/map.up.clusters.png")
# ggsave(out.path.map)
#width = 210, #A4
#height = 297, #A4
#units = "mm")
```

## Mapping median upload speeds for appendix 2019 and 2020

```{r}

# upload 2020
ts.up2020median <- TS2020 %>%
  group_by(LAD19NM) %>%
  summarise(mean.up = median(speedup))

ts.up2019median <- TS2019 %>%
  group_by(LAD19NM) %>%
  summarise(mean.up = median(speedup))

# scatter plots
sp2020 <- ggplot(ts.up2020median, 
       aes(x=mean.up)) + 
  geom_histogram() +
  geom_vline(aes(xintercept=mean(mean.up)), # This line of code adds a vertical line to represent the mean
             color="blue", linetype="dashed", size=1) +
  xlim(0, 20000) +
  ylab("count 2020")

sp2019 <- ggplot(ts.up2019median, 
       aes(x=mean.up)) + 
  geom_histogram() +
  geom_vline(aes(xintercept=mean(mean.up)), # This line of code adds a vertical line to represent the mean
             color="blue", linetype="dashed", size=1) +
  xlim(0, 20000) +
  ylab("count 2019")

sp20192020 <- grid.arrange(sp2019, sp2020, ncol = 1, nrow = 2) #legend

out.plot <- paste0(path, "/paper/v2_taylor_francis/figures/sc2019_2020.png")
ggsave(out.plot, sp20192020)

la.f.up <- broom::tidy(la, region = "lad19nm")
la.f.up <- merge(la.f.up, ts.up2020median, by.x = "id", by.y = "LAD19NM")
la.f.up <- la.f.up %>% 
  rename(mean.up2020 = mean.up)
la.f.up <- merge(la.f.up, ts.up2019median, by.x = "id", by.y = "LAD19NM")
la.f.up <- la.f.up %>% 
  rename(mean.up2019 = mean.up)
la.f.up <- la.f.up[order(la.f.up$order),] # if i don't order merge.nuts.f loses order and the map has gaps

# Already defined
# using world.cities from `maps`
# cities <- world.cities %>% filter(country.etc=="UK")

no_classes <- 4
quantiles2019 <- quantile(ts.up2019median$mean.up, 
                      probs = seq(0, 1, length.out = no_classes + 1), na.rm = T)
la.f.up$quantile2019 <- cut(la.f.up$mean.up2019,
                             breaks = quantiles2019,
                             labels = c("1st quartile", "2nd quartile", "3rd quartile", "4th quartile"),
                             right = T)
quantiles2020 <- quantile(ts.up2020median$mean.up, 
                      probs = seq(0, 1, length.out = no_classes + 1), na.rm = T)
la.f.up$quantile2020 <- cut(la.f.up$mean.up2020,
                             breaks = quantiles2020,
                             labels = c("1st quartile", "2nd quartile", "3rd quartile", "4th quartile"),
                             right = T)

map2019 <- ggplot(la.f.up, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = quantile2019)) + #mean.up2019
  #labs(title = "Upload clusters") +
  scale_fill_brewer(palette = "Greens") +
  geom_text_repel( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat, label=name), size=4) +
  geom_point( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat), color="black", size=1) +
  guides(fill=guide_legend(title="Median upload speed")) + #, 2019
  theme_void() #+ 
  # theme(legend.text = element_text(size = 11), legend.position="bottom",
  #       legend.key.size = unit(0.25, "cm"), legend.key.width = unit(0.25,"cm"), 
  #       legend.box = "horizontal",
  #       legend.margin=margin(0,0,0,0), legend.box.margin=margin(-40,20,40,20), # This is to bring the legend closer to the map for the grid
  #       plot.margin = unit(c(0, 1.5, 0, -1.5), "cm"))

map2020 <- ggplot(la.f.up, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = quantile2020)) +
  #labs(title = "Upload clusters") +
  scale_fill_brewer(palette = "Greens") +
  geom_text_repel( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat, label=name), size=4) +
  geom_point( data=cities %>% arrange(pop) %>% tail(10), aes(x=long, y=lat), color="black", size=1) +
  guides(fill=guide_legend(title="Median upload speed, 2020")) +
  theme_void()

# get legend
legend <- get_legend(map2019)

# remove legends
map2019 <- map2019 + theme(legend.position = "map2019")
map2020 <- map2020 + theme(legend.position = "map2020")

up20192020 <- grid.arrange(map2019, map2020, ncol = 2, nrow = 2) #legend

out.plot <- paste0(path, "/paper/v2_taylor_francis/figures/up2019_2020.png")
ggsave(out.plot, up20192020)

# plot_grid(couk.pop2000, couk.pop2010, noncouk.pop2000, noncouk.pop2010, legend, nrow = 3, ncol = 2,
#           align = "h", axis = "l", 
#           #labels = c(".co.uk / pop., 2000", ".co.uk / pop., 2010", "non .co.uk / pop., 2000", "non .co.uk / pop., 2010", ""), 
#           #label_size = 12,
#           greedy = T,
#           rel_heights = c(1, 1, .3)) # this is the relative position of the 3 lines

```{r, eval=FALSE, include=FALSE}
# test for ploty

library(plotly)

p <- 
  ggplotly(test, layerData = 1, 
           originalData = T,
           add_trace(z=~cluster.tests))#, tooltip="text")

```{r, eval=FALSE, include=FALSE}
# leaflet maps
